---
title: "Models"
output:
  md_document:
    variant: markdown_github
  word_document:
  - default
  html_document:
    fig_caption: yes
    css: assets/custom.css
---

_This script generates the summary tables and reports statistics for the 
models in the article._

```{r Knitr Preamble, echo = FALSE, warning = FALSE, message = FALSE}
library("knitr")

options(stringsAsFactors = FALSE)
opts_knit$set(root.dir = "../")
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 6.5,
  fig.height = 4.5)
```


```{r Preamble}
library("magrittr")
library("dplyr")
library("broom")
library("lme4")
library("ggplot2")

load("data/models.Rdata")

# Nearly all of the custom functions are in the 00_utils_formatting.R script
source("R/00_utils_formatting.R")
source("R/00_lookr_imports.R")

# Table to help convert orthogonal time values back to milliseconds
times <- read.csv("data/model_data.csv") %>% 
  select(Time, ot1) %>% 
  unique

# Extract values from an lme4 model
tidy_model <- . %>% 
  augment %>% 
  tbl_df %>% 
  rename(Fitted = .fitted) %>%
  # Include millisecond time values from above
  left_join(times, by = "ot1")

# Plot an lme4 model
plot_model <- function(model) {
  m <- tidy_model(model)

  # Format title
  l1 <- "Observed fixation probabilities and standard errors (symbols)"
  l2 <- "and growth curve model estimates (lines)"
  title_lines <- sprintf("%s\n%s", l1, l2)
  
  ggplot(m, aes(x = Time, y = elogit, color = Condition)) +
    # Observed values
    stat_summary(fun.data = mean_se, geom = "pointrange") +
    # Model fits
    stat_summary(aes(y = Fitted), fun.y = mean, geom = "line") +
      labs(x = "Time since target word onset (ms)",
           y = "Emp. log-odds of looking to target",
           title = title_lines)
}
```


## Model Output

`lme4::summary` of the final model:

```{r}
# Called baseline now bc it's the baseline for the model comparisons later
baseline <- models$main$m_cond_ranef

summary(baseline)
```

```{r}
plot_model(baseline)
```



## Write up

```{r}
# Prepare table to support easy in-line printing of equations
params <- baseline %>% tidy_lme4 %>% rename(B = Estimate)
params$subscript <- c(paste0(0:3, 0), paste0(0:3, 1))
params$Parameter %<>% 
  str_replace(".Intercept.", "Intercept") %>%
  str_replace("Conditionfacilitating", "faci") %>%
  str_replace(":", "_")
row.names(params) <- params$Parameter

# Shortcut for inline reporting from the above table
report_row <- function(row_name) report_fixef_row(params, row_name)

# Pre-calculate intercept as proportion
b0 <- params["Intercept", "B"]
b0_prop <- b0 %>% inv_logit %>% round(2) %>% remove_leading_zero

# Pre-calculate effect of condition as proportion
b0_faci <- params["faci", "B"]
b0_increase <- inv_logit(b0 + b0_faci) - inv_logit(b0)
b0_increase %<>% round(2) %>% remove_leading_zero()
```

The log-odds of looking to target in the neutral condition over the entire 
analysis window were estimated by the intercept term, 
_&gamma;_<sub>00</sub>&nbsp;=&nbsp;`r fixed_digits(b0, 2)` 
(proportion:&nbsp;`r b0_prop`). The linear, quadratic, and cubic orthogonal 
time terms were all significant, confirming a curvilinear, sigmoid-shape change 
in looks to target over time.

There was a significant increase in accuracy in the facilitating condition 
[`r report_row("faci")`] such that the overall proportion of looking to target 
increased by `r b0_increase`. There was a significant effect of condition on 
the quadratic term [`r report_row("ot2_faci")`]. These effects can be 
interpreted geometrically: The larger intercept increases the overall area 
under the curve, and the reduced quadratic effect decreases the bowing on the 
center of the curve, allowing the facilitating curve to obtain its positive 
slope earlier than the neutral curve. There was not a significant effect of 
condition on the linear term [`r report_row("ot1_faci")`], indicating that the 
overall slopes of the growth curves did not differ significantly. These 
condition effects result in the two curves being roughly parallel at the 
center of the analysis window but with points phase-shifted by 100 ms. 



## Tables

### Fixed effects

```{r, results = "asis"}
pretty_fixed_effects <- baseline %>% 
  tidy_lme4 %>% 
  mutate(p = format_pval(p), Parameter = fix_param_names(Parameter)) %>% 
  mutate_each(funs(format_fixef_num), Estimate:t) %>% 
  rename(`_t_` = t, `_p_` = p)

# Include gammas (Gij) after each parameter name
subs <- c(paste0(0:3, 0), paste0(0:3, 1))
var_labels <- parenthesize(paste0(emphasize("&gamma;"), subscript(subs)))
pretty_fixed_effects$Parameter %<>% paste(., var_labels)

pretty_fixed_effects %>% 
  kable(format = "pandoc", caption = "Model fixed effects", 
        align = str_tokenize("lrrrr"))
```

### Random effects

```{r, results = "asis"}
ranef_table <- baseline %>% 
  tidy_ranef_summary %>% 
  # Format the numbers
  mutate_each(funs(format_fixef_num), vcov, sdcor) %>%
  mutate_each(funs(format_cor), -var1, -grp, -vcov, -sdcor) %>%
  sort_ranef_grps %>%
  # Format variable names and group names
  mutate(var1 = fix_param_names(var1) %>% blank_nas,
         grp =  blank_same_as_last(grp) %>% fix_param_names) %>% 
  rename(Group = grp, Parameter = var1, Variance = vcov, SD = sdcor)

# Correlation columns need names with characters so that pandoc can align them
names(ranef_table)[5:8] <- c("Correlations", "&nbsp;", " &nbsp;", "  &nbsp;")

# Include Uij, Wijk, Rtjk coefficients in Estimates column. 
# Procedure: Make subscripts, prefix with grouping letter, wrap in parens,
# prefix with space for non-residual terms
child_j <- paste0(0:3, emphasize("j")) %>% 
  subscript %>% 
  paste_onto(emphasize("U")) %>% 
  parenthesize %>% 
  paste_onto(" ")

child_group_jk <- paste0(0:3, emphasize("jk")) %>% 
  subscript %>% 
  paste_onto(emphasize("W")) %>% 
  parenthesize %>% 
  paste_onto(" ")

residual_tjk <- paste0(emphasize("R"), subscript(emphasize("tjk")))

# Attach onto Estimates column
ranef_table$Parameter %<>% paste0(., c(child_j, child_group_jk, residual_tjk))

ranef_table %>% 
  kable(caption = "Model random effects", format = "pandoc", 
        align = str_tokenize("llrrrrrr"))
```



## Model Comparisons

The effects are age and vocabulary are tested by using nested model comparisons 
via the `anova` function. 


### Age Models

```{r Age models, results='asis', warning=FALSE}
# Table-printing shortcut for these anova pipelines
anova_kable <- function(model, caption) {
  kable(model, caption = caption, format = "pandoc", digits = 2) %T>% print
}

# Include model without age as baseline for comparisons
age_models <- c(baseline, models$age$age_time)
age_cond_models <- c(baseline, models$age$age_time_cond)

# Using do.call because models are stored in a list
age_anova1 <- age_models %>% 
  do.call(anova, .) %T>% 
  anova_kable(caption = "Age models")

age_anova2 <- age_cond_models %>% 
  do.call(anova, .) %T>% 
  anova_kable(caption = "Age x Condition models")
```


### Vocabulary models

```{r, results = "asis"}
# Include model without vocab as baseline for comparisons
cdi_models <- c(baseline, models$cdi$cdi_time)
cdi_cond_models <- c(baseline, models$cdi$cdi_time_cond)

cdi_anova1 <- cdi_models %>% 
  do.call(anova, .) %T>% 
  anova_kable(caption = "Vocabulary models")

cdi_anova2 <- cdi_cond_models %>% 
  do.call(anova, .) %T>% 
  anova_kable(caption = "Vocabulary x Condition models")
```


### Write up for article

Participant-level variables were tested by comparing nested models. There was
no effect of vocabulary size on the intercept 
(`r pretty_chi_result(cdi_anova1, "MODEL2")`), nor did vocabulary size interact 
with the condition effect (`r pretty_chi_result(cdi_anova2, "MODEL2")`). 
There was also no effect of age on the intercept term 
(`r pretty_chi_result(age_anova1, "MODEL2")`), nor did age interact with 
condition (`r pretty_chi_result(age_anova2, "MODEL2")`). Model fit did not 
significantly improve when vocabulary size or age were allowed to interact with 
Time or Time-by-Condition parameters.
