---
output:
  html_document:
    fig_caption: yes
    css: assets/custom.css
  md_document:
    variant: markdown_github
csl: assets/apa.csl
bibliography: assets/refs.bib
---

_This script fills in variables used in paragraphs in the article._

```{r Preamble, echo = FALSE, warning = FALSE, message = FALSE}
library("knitr")
library("magrittr")
library("dplyr", warn.conflicts = FALSE)

options(stringsAsFactors = FALSE, digits = 4)
opts_knit$set(root.dir = "../")
opts_chunk$set(
  echo = FALSE, 
  warning = FALSE, 
  message = FALSE, 
  fig.width = 6.5, 
  fig.height = 4.5)

```


```{r Helpers}
format_range <- function(values, format = "%.1f") {
  template <- paste0(format, "--", format)
  sprintf(template, min(values), max(values))
}

# Equation with non-breaking spaces
`%nb_eq%` <- function(x, y) {
  paste0(x, "&nbsp;=&nbsp;", y)
}
```


## Participants

```{r E1 Counts}
kids <- read.csv("data/subj.csv")
kids_in_models <- kids %>% filter(is.na(Exclude))

n_boys <- read.csv("data/genders.csv") %>% 
  filter(Gender == "M") %>% 
  extract2("n")

mean_age <- kids_in_models$Age %>% mean %>% round(1) 
age_range_p <- kids_in_models$Age %>% range %>% format_range

# Used to have qdap replace the numerals with wrtten-out words, but that
# required too many libraries.
breakdown <- kids$Exclude %>% table %>% as.list
n_dropped <- breakdown %>% unlist %>% sum
n_inattentive <- breakdown[["no-trials"]] + breakdown[["too-few-trials"]]
n_mistracking <- breakdown[["excessive-missing-data"]]
```

`r nrow(kids_in_models)` 18 to 24-month-olds (`r "_M_" %nb_eq% mean_age`, 
`r "range" %nb_eq% age_range_p`, `r n_boys` male) participated in this study. An 
additional `r n_dropped` children were excluded from the analyses due to 
inattentiveness (`r n_inattentive`) or having more than 50% missing data during 
non-filler trials (`r n_mistracking`).  



### Software sentence

```{r}
r_vers <- sprintf("%s.%s", R.version$major, R.version$minor)
```

Analyses were performed in `R` (vers. `r r_vers`) with the `lme4` package 
[vers. `r packageVersion("lme4")`; @lme4]. 

***
