---
title: "Stimuli"
author: "Tristan Mahr"
date: "December 11, 2015"
output: 
  html_document: 
    keep_md: yes
---

```{r, echo = FALSE}
library("knitr")
opts_chunk$set(comment = "#>")
```

## Design Summary

`trials.csv` contains a table documenting the experimental design. There is one
row per experimental trial designed. 

The columns of the table indicate:

* `Block`: The experiment was administer using two blocks of trials. This number 
  indicates which block includes this trial.
* `TrialNo`: The number of the trial within the block. Trials are numbered in 
  the order in which they are administered.
* `Condition`: Experimental condition.
* `WordGroup`: Which yoked pair of words were presented.
* `TargetWord`: The word named during that trial.
* `TargetImage`: The side of the screen ("ImageL" = left, "ImageR" = right) 
   containing the target image.
* `DistractorImage`: The side of the screen ("ImageL" = left, "ImageR" = right) 
   containing the distractor image.
* `ImageLFile`: Filename of the image presented on the left side of the screen.
* `ImageRFile`: Filename of the image presented on the left side of the screen.
* `CarrierWord`: Word used to start the carrier phrase.
* `CarrierPitch`: For variety, we use two versions of each carrier phrase 
  starter: One with a high ("hi") pitch and one with a low ("lo") pitch.
* `PromptFile`: Filename of the recording used as the prompt during the trial.
* `AttentionGetterFile`: Filename of the attention-getter/reinforcer that played 
  at the end of each trial.

The output below shows the first few values ("Observations") in each column
("Variables"):

```{r, message = FALSE}
library("readr")
library("dplyr")
library("knitr")
stim_set <- read_csv("trials.csv")
glimpse(stim_set, width = 70)
```

### Pivot Tables

We can check the balance of the trials by counting the trials under different
kinds of grouping. 

Number of times each word is the target in each condition:

```{r}
stim_set %>% 
  group_by(Condition, WordGroup, TargetWord) %>% 
  tally %>% 
  kable
```

Number of times the left or right side of the screen contained the target in
each condition:

```{r}
stim_set %>% 
  group_by(Condition, TargetImage) %>% 
  tally %>% 
  kable
```
